Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-02-24 docs/00-manuscripts/ieee/performance-best-per-learner.tex
line-endings
update workflowr site for submission
update latex performance tables

% latex table generated in R 3.6.1 by xtable 1.8-3 package
\begin{table}[ht!]
\centering
\caption{Best performance of each learner across any task and filter method.} 
\label{tab:best-learner-perf}
\scalebox{0.9}{
\begin{tabular}{rlllrr}
  \hline
 & Task & Model & Filter & RMSE & SE \\ 
  \hline
1 & HR-NRI & SVM & Car & 27.98 & 19.19 \\ 
  2 & HR-NRI & RF & Car & 31.08 & 17.09 \\ 
  3 & NRI-VI & XGBOOST & Relief & 32.10 & 17.73 \\ 
  4 & NRI & Ridge-CV & No Filter & 32.97 & 7.24 \\ 
  5 & HR & Lasso-CV & No Filter & 45.96 & 18.35 \\ 
   \hline
\end{tabular}
}
\end{table}

>>>>

% latex table generated in R 4.0.4 by xtable 1.8-4 package
\begin{table}[ht!]
\centering
\caption{Best performance of each learner across any task and filter method, sorted ascending by RMSE} 
\label{tab:best-learner-perf}
\scalebox{0.9}{
\begin{tabular}{rlllrrr}
  \hline
 & Task & Model & Filter & rsq & RMSE & SE \\ 
  \hline
1 & NRI & SVM & Info Gain & -0.07 & 28.03 & 19.13 \\ 
  2 & HR-NRI & XGBoost & Car & -0.30 & 31.02 & 17.63 \\ 
  3 & VI & Lasso-MBO & No Filter & -5.97 & 31.11 & 14.91 \\ 
  4 & NRI & Ridge-MBO & No Filter & -0.18 & 31.16 & 15.03 \\ 
  5 & NRI & RF & Car & -5.97 & 32.14 & 15.97 \\ 
   \hline
\end{tabular}
}
\end{table}

### 2021-02-24 docs/00-manuscripts/ieee/tune-perc-sel-features.tex
update tables and figures
update latex performance tables

% latex table generated in R 3.6.1 by xtable 1.8-3 package
\begin{table}[ht!]
\centering
\caption{Selected feature portions during tuning for selected learner-filter settings across folds for task HR-NRI-VI, sorted ascending by RMSE} 
\label{tab:tune-perc-sel-features}
\begin{tabular}{llrr}
  \toprule
Learner & Plot & Features (\%) & RMSE \\ 
  \midrule
\midrule\multirow{4}{*}{\textbf{RF Car}} & Laukiz1 & 0.00443 & 27.48 \\ 
   & Oiartzun & 0.00004 & 37.20 \\ 
   & Luiando & 0.00002 & 36.98 \\ 
   & Laukiz2 & 0.03037 & 15.39 \\ 
  \midrule\multirow{4}{*}{\textbf{XGB Borda}} & Laukiz1 & 0.00604 & 15.00 \\ 
   & Oiartzun & 0.68227 & 36.15 \\ 
   & Luiando & 0.99513 & 38.19 \\ 
   & Laukiz2 & 0.99976 & 29.62 \\ 
  \midrule\multirow{4}{*}{\textbf{SVM Relief}} & Laukiz1 & 0.00017 & 35.50 \\ 
   & Oiartzun & 0.71146 & 37.48 \\ 
   & Luiando & 0.70672 & 14.89 \\ 
   & Laukiz2 & 0.94696 & 37.19 \\ 
   \bottomrule
\end{tabular}
\end{table}

>>>>

% latex table generated in R 4.0.3 by xtable 1.8-4 package
\begin{table}[ht!]
\centering
\caption{Selected feature portions during tuning for selected learner-filter settings across folds for task HR-NRI-VI, sorted ascending by RMSE} 
\label{tab:tune-perc-sel-features}
\begin{tabular}{llrrr}
  \toprule
Learner & Test Plot & Features (\%) & \# & RMSE \\ 
  \midrule
\multirow{4}{*}{\specialcell{RF \\ Car}} & Laukiz1 & 0.00485 & 3 & 27.77 \\ 
   & Oiartzun & 0.00002 & 1 & 37.20 \\ 
   & Luiando & 0.02875 & 9 & 15.57 \\ 
   & Laukiz2 & 0.04573 & 21 & 38.63 \\ 
  \midrule\multirow{4}{*}{\specialcell{XGB \\ Borda}} & Laukiz1 & 0.50710 & 284 & 38.19 \\ 
   & Oiartzun & 0.73142 & 364 & 29.85 \\ 
   & Luiando & 0.94800 & 286 & 36.91 \\ 
   & Laukiz2 & 0.23877 & 108 & 15.33 \\ 
  \midrule\multirow{4}{*}{\specialcell{SVM \\ Relief}} & Laukiz1 & 0.19391 & 109 & 14.85 \\ 
   & Oiartzun & 0.00025 & 1 & 35.31 \\ 
   & Luiando & 0.04491 & 14 & 36.25 \\ 
   & Laukiz2 & 0.00015 & 1 & 37.48 \\ 
   \bottomrule
\end{tabular}
\end{table}
